\documentclass{article}

\input{preamble}
\input{macros}
\input{letterfonts}
\begin{document}
\pagenumbering{gobble}
\begin{center}
    {\LARGE \textbf{Letter of Appeal for Writing the PhD Dissertation in English}}
\end{center}

\vspace{1cm} % Adjust spacing below the title if needed
Dear Committee Members,
\vspace{1cm}

I hope this message finds you well. I am writing to formally request permission to write my PhD thesis in English.
As an international student and non-native speaker of Slovenian, I believe that completing my thesis in English would be beneficial for both academic and practical reasons.
Firstly, English is the primary language in my field of study, and the majority of relevant literature, research articles, and publications are available in English.
Writing my thesis in English would enable me to engage more directly with this body of work and ensure that my research is positioned within the global academic discourse.
Secondly, my supervisor, Assoc. Prof. Dr. Rainer Oliver Kaltenbaek, who is also a non-native speaker of Slovenian, has advised that conducting and evaluating the research in 
English would facilitate clearer communication and collaboration throughout the thesis process. Furthermore, writing in English would allow for smoother peer review 
and potential publication in international journals.
Lastly, most, if not all of the literature that I am using in my doctoral studies are in English and I believe it would slow down my progress to translate
all of the terminoligy and nomenclature to Slovenian.
I greatly appreciate your understanding and consideration of this request. I am confident that writing my thesis in English will enhance its academic 
impact and contribute positively to my development as a researcher. Please let me know if further clarification or documentation is required to support this appeal.
Thank you for your time and attention. I look forward to your response.

\vspace{1cm}
Yours sincerely,\\
Adrian Udovičić\\
Faculty of Mathematics and Physics, Department of Physics\\
adrian.udovicic@fmf.uni-lj.si
\end{document}
